Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-29 paper/ms.tex
Add thincolor, thickcolor, and halocolor commands

@@

We now repeat the procedure but continuously changing the error in the $z$ and
$x$ components. In Figure~\ref{fig:many_orbit_wrong_ref}, we report the 95\uth
minus 5\uth percentile divided by the true action value for three different
orbits. The thick (brown) orbit is exactly the same as in
Figure~\ref{fig:one_orbit_wrong_ref}, and we also consider the thin and halo
orbits (pink and blue, respectively) from Table~\ref{tab:orbits}.

@@

Figure~\ref{fig:Rn_mc} is most informative for the low $J_z$ orbit (blue). The
neighborhood around $\sim100\Msun$ clusters can be as small as $\sim300\,\pc$
but up to $\sim1.2\,\kpc$ for m12i and m12f, though the situation is
marginally better for m12m with values ranging from $\sim0.8\,\kpc$ to
$\sim3\,\kpc$. The neighborhood values steadily increase with $m_c$, topping
out at $\sim5\,\kpc$ for $\sim10^4\,\Msun$ clusters in m12i and m12f. In m12m,
the neighborhood value reaches the maximum allowed of $16.4\,\kpc$ for
clusters of mass $\sim800\,\Msun$. The interpretation of this is that the
expected action space dispersion is so high for such high mass clusters that
the measured $z$~offset is not large enough throughout the entire galaxy to be
important.

@@

\begin{figure*}
\plotone{fig/Rn_vs_mc.pdf}
\caption{The neighborhood around an open cluster of mass $m_c$ for our three
orbits (blue, orange, and red) and for each of the FIRE galaxies considered
here --- m12i, m12f, and m12m ({\em left}, {\em center}, and {\em right}
panels, respectively). Given the $z$ offset for a cluster of mass $m_c$
computed in Figure~\ref{fig:cluster_offset}, we convert this to a chord length
using the result from Figure~\ref{fig:range_deltaphi} and plot as a solid blue
line. We interpret this chord length as the ``neighborhood'' around the
cluster, i.e. the distance from the cluster one could go before the $J_z$
error induced by our midplane effect is comparable to the intrinsic action
dispersion of the cluster. When the $z$ offset is larger than the maximum
range in Figure~\ref{fig:range_deltaphi}, we report the maximum chord length
($2\times8.2\,\kpc$). We aso report the same procedure but using the
$\pm1\sigma$ lines from Figure~\ref{fig:range_deltaphi}, which we plot here as
dashed lines. For the medium- and high-$J_z$ orbits (orange and red), the
neighborhood is quite large and thus the effect is negligible. However, for
the low-$J_z$ orbit (blue), which is closest to the orbits of nearby open
clusters (see Table~\Gus{x}), the neighborhood is only a few hundred $\pc$ for
low-mass clusters.}
\label{fig:Rn_mc}
\end{figure*}

>>>>

\newcommand{\thincolor}{pink}
\newcommand{\thickcolor}{brown}
\newcommand{\halocolor}{blue}

@@

We now repeat the procedure but continuously changing the error in the $z$ and
$x$ components. In Figure~\ref{fig:many_orbit_wrong_ref}, we report the 95\uth
minus 5\uth percentile divided by the true action value for three different
orbits. The thick (\thickcolor) orbit is exactly the same as in
Figure~\ref{fig:one_orbit_wrong_ref}, and we also consider the thin and halo
orbits (\thincolor and \halocolor, respectively) from Table~\ref{tab:orbits}.

@@

Figure~\ref{fig:Rn_mc} is most informative for the thin orbit (\thincolor).
The neighborhood around $\sim100\Msun$ clusters can be as small as
$\sim300\,\pc$ but up to $\sim1.2\,\kpc$ for m12i and m12f, though the
situation is marginally better for m12m with values ranging from
$\sim0.8\,\kpc$ to $\sim3\,\kpc$. The neighborhood values steadily increase
with $m_c$, topping out at $\sim5\,\kpc$ for $\sim10^4\,\Msun$ clusters in
m12i and m12f. In m12m, the neighborhood value reaches the maximum allowed of
$16.4\,\kpc$ for clusters of mass $\sim800\,\Msun$. The interpretation of this
is that the expected action space dispersion is so high for such high mass
clusters that the measured $z$~offset is not large enough throughout the
entire galaxy to be important.

@@

\begin{figure*}
\plotone{fig/Rn_vs_mc.pdf}
\caption{The neighborhood around an open cluster of mass $m_c$ for the thin,
and thick orbits (\thincolor and \thickcolor, respectively; see
Table~\ref{tab:orbits}) and for each of the FIRE galaxies considered here ---
m12i, m12f, and m12m ({\em left}, {\em center}, and {\em right} panels,
respectively). Given the $z$ offset for a cluster of mass $m_c$ computed in
Figure~\ref{fig:cluster_offset}, we convert this to a chord length using the
result from Figure~\ref{fig:range_deltaphi} and plot as a solid blue line. We
interpret this chord length as the ``neighborhood'' around the cluster, i.e.
the distance from the cluster one could go before the $J_z$ error induced by
our midplane effect is comparable to the intrinsic action dispersion of the
cluster. When the $z$ offset is larger than the maximum range in
Figure~\ref{fig:range_deltaphi}, we report the maximum chord length
($2\times8.2\,\kpc$). We aso report the same procedure but using the
$\pm1\sigma$ lines from Figure~\ref{fig:range_deltaphi}, which we plot here as
dashed lines. For the medium- and high-$J_z$ orbits (orange and red), the
neighborhood is quite large and thus the effect is negligible. However, for
the low-$J_z$ orbit (blue), which is closest to the orbits of nearby open
clusters (see Table~\Gus{x}), the neighborhood is only a few hundred $\pc$ for
low-mass clusters.}
\label{fig:Rn_mc}
\end{figure*}
